\documentclass[11pt, a4paper]{article}

% --- UNIVERSAL PREAMBLE BLOCK ---
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2cm, right=2cm]{geometry}
\usepackage{fontspec}
\usepackage[english, bidi=basic, provide=*]{babel}
\babelprovide[import, onchar=ids fonts]{english}
\babelfont{rm}{Noto Sans}

\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}

\definecolor{vanguardBlue}{RGB}{0, 43, 92}
\titleformat{\section}{\large\bfseries\color{vanguardBlue}}{}{0em}{}[\titlerule]

\begin{center}
    {\Huge \textbf{MEX ROBERT}} \\
    \vspace{2mm}
    \textbf{Lead Blockchain Security Engineer | Founder of IceGods Ecosystem} \\
    \small \href{mailto:mexrobert@example.com}{Email} | \href{https://t.me/ICEGODSICEDEVIL}{Telegram: @ICEGODSICEDEVIL} | \href{https://github.com/ICEDEVILS}{GitHub: ICEDEVILS}
\end{center}

\section{Professional Summary}
Senior Web3 Architect specializing in automated security frameworks and high-frequency blockchain monitoring. Developed the \textbf{Vanguard SAI-838 Engine}, a proprietary shadow-audit tool for institutional Telegram and Web3 infrastructures.

\section{The IceGods Ecosystem (Live Deployments)}
\begin{itemize}
    \item \textbf{Vanguard Security Engine:} Institutional auditor with HECD entropy detection.
    \item \textbf{ChainPilot Signal Engine:} Autonomous whale-tracking and trade signal generation.
    \item \textbf{MEX WarSystem:} Real-time Ethereum/Solana mempool analyzer.
    \item \textbf{IceGods Bridge-Eyes:} Monitoring cross-chain institutional asset flow.
\end{itemize}

\section{Core Technical Arsenal}
\textbf{Languages:} Python (Expert), Node.js, React, LaTeX, SQL \\
\textbf{Specializations:} High-Entropy Callback Detection (HECD), Automated SAI Reporting, Helius RPC, Web3.py, Cloud Infrastructure (Render/Docker).

\section{Services \& Licensing}
\begin{itemize}
    \item \textbf{Custom Bot Infrastructure:} Scalable, secure Telegram automation.
    \item \textbf{SAI Compliance Audits:} Deep logic analysis for crypto startups.
    \item \textbf{Asset Recovery Engines:} Specialized monitoring for compromised wallets.
\end{itemize}

\vfill
\begin{center}
    \footnotesize \textit{This document is typeset according to Vanguard SAI 838 Institutional Standards.}
\end{center}

\end{document}
